\documentclass{tufte-handout}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{mathpazo}
\usepackage{booktabs}
\usepackage{microtype}

\pagestyle{empty}


\title{Word Ladders Report}
\author{Alice Cooper and Bob Marley}

\begin{document}
  \maketitle

  \section{Results}

  Our implementation produces the expected results on all input--output file pairs, except {\tt words-50.txt}, where our code reports distance 12 from zombi to aargh.
  We have no idea why this happens.%
  \sidenote{%
  Complete the report by filling in your correct names,
  filling in the parts marked $[\ldots]$,
  and changing other parts wherever necessary.
  For instance, if your implementation passes all tests, then write that.
  Remove the sidenotes in your final hand-in.
  }

  On input {\tt words-5757.txt}, a shortest path from aargh to zombi of length 3 is the following:
  \begin{quotation}
    aargh, dogma, gonad, zombi   \sidenote{Correct and replace as required.}
  \end{quotation}

  \section{Implementation details}

  We build the graph's edges by iterating over all [$\ldots$]%
  \sidenote{%
  Explain what you do.
  Be very brief.
  Three sentences are a lot.}
  The running time for graph construction is $O((n^3+\log^2 m)\cos w)$.\sidenote{%
  Replace as necessary.
  Use $n$ for the number of vertices,
    $m$ for the number of edges in the finished graph, and $w$ for the length of the words.
    Note that we alsways have $w=5$ in our inputs, but it still makes sense to make the word length visible in the running time.}

  The total running time of our implemenation (including graph construction and traversal) is [$\ldots$].


\end{document}
