\documentclass{tufte-handout}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{mathpazo}
\usepackage{booktabs}
\usepackage{microtype}

\pagestyle{empty}


\title{Stable Matching Report}
\author{Alice Cooper and Bob Marley}

\begin{document}
  \maketitle

  \section{Results}

  Our implementation produces the expected results on all input--output file pairs, except {\tt sm-random-100.txt}, where it matches 54 with 12 instead of 2.
  We have no idea why this happens.%
  \sidenote{%
  Complete the report by filling in your correct names,
  filling in the parts marked $[\ldots]$,
  and changing other parts wherever necessary.
  For instance, if your implementation passes all tests, then write that.
  Remove the sidenotes in your final hand-in.
  }

  On input {\tt sm-bbt-in.txt}, we produce the following matching:
  \begin{quotation}
    Sheldon--Amy, Rajesh--Penny, Howard--Bernadette, Leonard--Priya.  \sidenote{Replace with your results.}
  \end{quotation}

  \section{Implementation details}

  The men's preferences are stored in a left-leaning red--black B-tree with $B=12$ and no inverse anti-snails,%
  \sidenote{Replace with whatever data structure you actually use.}
   as described in Section 5.2 of Kleinberg and Tardos, \emph{Algorithms Design}, Addison--Wesley 2013.%
   \sidenote{If you refer to something, like a book or a stackexchange debate, or an external library, be professional about it.}
  The women's preferences are stored in a heap.\sidenote{Replace with whatever data structure you actually use.}

  We can check find a free man who has not proposed to every woman in time $[\ldots]$,
  because we store $[\ldots]$.

  With these data structures, our implementation runs in time $O(n\log n)$  \sidenote{Replace with your actual running time.}
  on inputs with $n$ men and $n$ women.


\end{document}
